\stktokens{}: Enforcing Well-Bracketed Control Flow and Stack Encapsulation Using Linear Capabilities

### 2020-12-28 popl-2019-journal-v/paper.tex
Add a paragraph on Laird's full abstraction result.

>>>>

\begin{jversion}
  The use of return pointers or capabilities in low-level languages is in many ways similar to lambda calculus terms in continuation passing style.
  When applying a CPS-translation to lambda terms, well-bracketedness can also be violated if continuations are invoked more than once.
  Enforcing well-bracketedness for CPS terms means enforcing that continuations are only used a single time and only in the right invocation, i.e.\ a form of linear (or more accurately, affine) usage of continuations must be enforced.
  One way to enforce this is by assigning well-chosen types to CPS-translated terms and researchers have proven effectiveness for two ways of doing this, in the form of a full-abstractness result for the CPS-translation.
  In both cases, correct usage of continuations is enforced by assigning well-chosen types to CPS-translated terms.
  In the case of \cite{laird_game_2005}, an affine type system is used to do this, while \citet{ahmed_equivalence-preserving_2011} use a form of answer-type polymorphism instead.
  These results are related to ours because they enforce well-bracketedness using a form of linearity of continuations or return capabilities, but there are also quite a few differences: the static nature of the enforcement, the low-level vs.\ high-level nature of the languages, the fact that LSE comes naturally in such a setting while we also have to enforce it.
Additionally, \citeauthor{ahmed_equivalence-preserving_2011} consider total languages and use a back-translation in two steps using an intermediate multi-language and \citeauthor{laird_game_2005} proves full abstraction using a fully abstract denotational semantics for source and target languages.
\end{jversion}
